Quantum parallel parallel Markov chain Monte Carlo

### 2021-11-25 main.tex
qqplot added to manu

>>>>

 \begin{figure}[!h]
	\centering
	\includegraphics[width=0.5\linewidth]{qqPlot.png}
	\caption{Empirical accuracy of quantum parallel MCMC (QPMCMC) for a 100 dimensional spherical Gaussian target.  We generate 100,000 samples using 2,000 proposals each iteration and remove the first 2,000 samples as burn-in.  The QQ (quantile-quantile) plot shows sample quantiles adhering closely to the theoretical quantiles.  Similar to the independent simulation shown in Figure \ref{fig:mcmcIterations}, here QPMCMC requires less than $7.2$\% of the usual number of target evaluations.}\label{fig:qq}
\end{figure}
